---
title: "outputs_inspection"
output: word_document
editor_options: 
  chunk_output_type: console
---

# Calibration outputs

5 replicated simulations

2 forest types: 

  - high altitude: pnigra, psylvestris, qpyrenaica
  
  - low altitude: phalepensis, ppinaster, qilex, qfaginea

```{r}
# Setup
# sim_name <- "pnigra_psylvestris_qpyrenaica_reg1_replicate_"
sim_name <- "phalepensis_ppinaster_qilex_qfaginea_reg1_replicate_"

# species_list <- c("pnigra", "psylvestris", "qpyrenaica")
species_list <- c("phalepensis", "ppinaster", "qilex", "qfaginea")

di <- "..."

ecoregion <- "Ecoregion 1"
nr_replicates <- 5
```

```{r setup, include = FALSE, echo = FALSE}
library(ggplot2)
library(tidyverse)
library(reshape)
library(ggrepel)

# Colors
library(RColorBrewer)
# display.brewer.all(colorblindFriendly = T)
# display.brewer.pal(n = 12, name = 'Paired')
# brewer.pal(12, 'Paired')

# Full palette: 
#   "#1F78B4" = dark blue
#   "#33A02C" = dark green
#   "#FB9A99" = pink
#   "#6A3D9A" = dark purple
#   "#FDBF6F" = light orange
#   "#FF7F00" = orange
#   "#E31A1C" = red
#   "#A6CEE3" = light blue
#   "#B2DF8A" = light green
#   "#FFFF99" = yellow
#   "#B15928" = brown
#   "#CAB2D6" = light purple

# Assign colors to species/groups
cols <- c("phalepensis" = "#1F78B4", # dark blue
          "pnigra" = "#33A02C", # dark green
          "ppinaster" = "#FB9A99",  # pink
          "psylvestris" = "#6A3D9A", # dark purple
          "qfaginea" = "#B15928", # brown
          "qilex" = "#FF7F00", # orange 
          "qpyrenaica" = "#E31A1C", # red
          "Junipers" = "#A6CEE3", # light blue
          "Shrubs" = "#B2DF8A", # light green
          "popnigra" = "#FFFF99") #  yellow
```

```{r, echo = FALSE}
# Create empty data frame to fill in with data
sim_years = c(1890:2099)
months_dec = c(0.00, 0.08, 0.17, 0.25, 0.33, 0.42, 0.50, 0.58, 0.67, 0.75, 0.83, 0.92)

simulation <- as.data.frame(expand.grid(Year = sim_years,
                                        Month = months_dec,
                                        Species = species_list)) %>%
  mutate(Time = Year + Month) %>% 
  dplyr::select(Time, Species)
```

```{r, echo = FALSE}
# Load and fetch data
all_site_data <- data.frame()

for (i in 1:nr_replicates) {
  site_data <- read.csv(paste(di, sim_name, i, "_site.csv", sep = "")) %>% # Load site data
    full_join(simulation, by = c("Species" = "Species", # Create empty rows for dead species
                                 "Time" = "Time")) %>%
    mutate(Replicate = i) %>% # Add replicate column
    dplyr::select(Replicate, Species, Time, Fol.gDW., Root.gDW., Wood.gDW., NetPsn.gC_m2_mo.)
  
  site_data[is.na(site_data)] <- 0
  
  site_data <- site_data %>%
    mutate(total_biomass_tn_ha = (Fol.gDW. + Root.gDW. + Wood.gDW.) / 100) %>%
    dplyr::select(Replicate, Species, Time, total_biomass_tn_ha, NetPsn.gC_m2_mo.)
  
  assign(paste("replicate", i, sep = ""), site_data)
  
  all_site_data <- rbind(all_site_data, site_data)
}
```

```{r, echo = FALSE}
# Add calendar month column
month_equiv <- data.frame(Month_dec = c(0.00, 0.08, 0.17, 0.25, 0.33, 0.42, 0.50, 0.58, 0.67, 0.75, 0.83, 0.92), 
                          Month = c(1,2,3,4,5,6,7,8,9,10,11,12))
```

# Biomass plots 

## Inspect replicates
```{r}
ggplot(all_site_data, aes(x = Time, y = total_biomass_tn_ha, group = Replicate)) +
  geom_line() +
  facet_wrap( ~ Species, ncol = 2) +
  theme_minimal()
```

At yearly scale: average among replicates and year
```{r, echo = FALSE}
# Calculate yearly averages and sd among replicates
yearly_agg_site <- all_site_data[,c(2:5)] %>%
  mutate(Year = floor(Time) - 1890) %>% # Create Year and Month_dec columns
  dplyr::select(Species, Year, total_biomass_tn_ha, NetPsn.gC_m2_mo.) %>%
  group_by(Species, Year) %>%
  summarise(AVG_biomass_tn_ha = mean(total_biomass_tn_ha),
            SD_biomass_tn_ha = sd(total_biomass_tn_ha),
            AVG_netpsn_gC_m2_mo = mean(NetPsn.gC_m2_mo.),
            SD_netpsn_gC_m2_mo = sd(NetPsn.gC_m2_mo.))

# Plot
plot_name <- "biomass.svg"
# svg(file = paste("...", sim_name, plot_name, sep = ""), width = 6, height = 4, pointsize = 12)

ggplot(yearly_agg_site, aes(x = Year, y = AVG_biomass_tn_ha, 
                    ymin = AVG_biomass_tn_ha - SD_biomass_tn_ha, 
                    ymax = AVG_biomass_tn_ha + SD_biomass_tn_ha, 
                    fill = Species)) +
  geom_ribbon(alpha=0.5) +
  geom_point(size = 0.1, aes(colour = Species)) +
  geom_line(aes(colour = Species)) +
  scale_color_manual(values=cols) +
  scale_fill_manual(values=cols) +
  theme_classic() +
  scale_y_continuous(bquote('Biomass ('*tn~ ha^-1*')'), limits = c(0, 150)) +
  scale_x_continuous("Time (years)") +
  theme(legend.position = "none", text = element_text (size = 13)) +
  theme(axis.text=element_text(size=14, face="bold"))

# dev.off()
```

# Photosynthesis

Inspect replicates
```{r}
ggplot(all_site_data, aes(x = Time, y = NetPsn.gC_m2_mo., color = as.factor(Replicate))) +
  geom_point(size = 0.2) +
  facet_wrap( ~ Species, ncol = 2) +
  theme_minimal() +
  theme(legend.position = "none")
```

At monthly scale: average among replicates and month
```{r, echo = FALSE}
# Calculate monthly averages of photosynthesis
month_agg_site <- all_site_data[,c(2:5)] %>%
  mutate(Year = floor(Time), Month_dec = round(Time - Year, digits = 2)) %>% # Create Year and Month_dec columns
  left_join(month_equiv) %>%
  dplyr::select(Species, Month, total_biomass_tn_ha, NetPsn.gC_m2_mo.) %>%
  group_by(Species, Month) %>%
  summarise(AVG_biomass_tn_ha = mean(total_biomass_tn_ha),
            SD_biomass_tn_ha = sd(total_biomass_tn_ha),
            AVG_netpsn_gC_m2_mo = mean(NetPsn.gC_m2_mo.),
            SD_netpsn_gC_m2_mo = sd(NetPsn.gC_m2_mo.))
```

```{r, echo = FALSE}
# ggplot(month_agg_site, aes(x = Month, y = AVG_netpsn_gC_m2_mo, 
#                     ymin = AVG_netpsn_gC_m2_mo - SD_netpsn_gC_m2_mo, 
#                     ymax = AVG_netpsn_gC_m2_mo + SD_netpsn_gC_m2_mo, fill = Species)) +
#   geom_point(size = 1, aes(colour = Species)) +
#   geom_line(aes(colour = Species)) +
#   # scale_color_manual(values=c("#F0E442", "#0072B2", "#D55E00", "#CC79A7")) +
#   scale_color_manual(values=c("#E69F00", "#56B4E9", "#009E73", "#CC79A7")) +
#   # geom_ribbon(alpha=0.5) +
#   geom_errorbar(width=.2, color = "grey") +
#   theme_minimal() +
#   scale_y_continuous("Net Photosynthesis (gC/m2·mo)", limits = c(0, 150)) +
#   scale_x_continuous("Month", breaks = c(1,2,3,4,5,6,7,8,9,10,11,12)) +
#   theme(legend.position = "bottom") +
#   ggtitle(paste("Net Photosynthesis", ecoregion, sep = " - "))

# ggplot(month_agg_site, aes(x = Month, y = AVG_netpsn_gC_m2_mo, 
#                     ymin = AVG_netpsn_gC_m2_mo - SD_netpsn_gC_m2_mo, 
#                     ymax = AVG_netpsn_gC_m2_mo + SD_netpsn_gC_m2_mo, fill = Species)) +
#   geom_point(size = 1, aes(colour = Species, shape = Species)) +
#   # geom_line(aes(colour = Species)) +
#   # scale_color_manual(values=c("#F0E442", "#0072B2", "#D55E00", "#CC79A7")) +
#   scale_color_manual(values=c("#E69F00", "#56B4E9", "#009E73", "#CC79A7")) +
#   # geom_ribbon(alpha=0.5) +
#   geom_errorbar(width=.2, color = "grey") +
#   theme_minimal() +
#   scale_y_continuous("Net Photosynthesis (gC/m2·mo)", limits = c(0, 150)) +
#   scale_x_continuous("Month", breaks = c(1,2,3,4,5,6,7,8,9,10,11,12)) +
#   theme(legend.position = "bottom") +
#   ggtitle(paste("Net Photosynthesis", ecoregion, sep = " - "))
```

At monthly scale: average among replicates and month - filtering for years 50-75
```{r, echo = FALSE}
# Calculate monthly averages of photosynthesis
month_agg_site <- all_site_data[,c(2:5)] %>%
  mutate(Year = floor(Time), Month_dec = round(Time - Year, digits = 2)) %>% # Create Year and Month_dec columns
  filter(Year %in% (1940:1965)) %>%
  left_join(month_equiv) %>%
  dplyr::select(Species, Month, total_biomass_tn_ha, NetPsn.gC_m2_mo.) %>%
  group_by(Species, Month) %>%
  summarise(AVG_biomass_tn_ha = mean(total_biomass_tn_ha),
            SD_biomass_tn_ha = sd(total_biomass_tn_ha),
            AVG_netpsn_gC_m2_mo = mean(NetPsn.gC_m2_mo.),
            SD_netpsn_gC_m2_mo = sd(NetPsn.gC_m2_mo.))

# Plot
plot_name <- "monthly_psn.jpeg"
# jpeg(file = paste("...", sim_name, plot_name, sep = ""), width=6, height=4, units="in", res=300)

ggplot(month_agg_site, aes(x = Month, y = AVG_netpsn_gC_m2_mo, 
                    ymin = AVG_netpsn_gC_m2_mo - SD_netpsn_gC_m2_mo, 
                    ymax = AVG_netpsn_gC_m2_mo + SD_netpsn_gC_m2_mo, fill = Species)) +
  geom_errorbar(width=.2, color = "grey") +
  geom_point(size = 1, aes(colour = Species)) +
  geom_line(aes(colour = Species)) +
  scale_color_manual(values=cols) +
  scale_fill_manual(values=cols) +
  theme_classic() +
  scale_y_continuous(bquote('Net Photosynthesis ('*gC~ m^-2~ month^-1*')'),
                     limits = c(0, 150)) +
  scale_x_continuous("Month", 
                     breaks = c(1,2,3,4,5,6,7,8,9,10,11,12)) +
  theme(legend.position = "bottom", text = element_text (size = 13)) +
  theme(axis.text=element_text(size=14, face="bold"))

# dev.off()
```
